# D1 Assignment {#sec-day-1-assignments}

```{r}
#| echo: false
source("_common.R")
library(ggplot2)
library(tidyverse)
eammi2 <- read.csv("data/EAMMi2-CleanData.csv")
```

1.  The `mpg` data frame that is bundled with the ggplot2 package contains `r nrow(mpg)` observations collected by the US Environmental Protection Agency on 38 car models. Which variables in `mpg` are categorical? Which variables are numerical? (Hint: Type `?mpg` to read the documentation for the dataset.) How can you see this information when you run `mpg`?

2.  Make a scatterplot of `hwy` vs. `displ` using the `mpg` data frame. Next, map a third, numerical variable to `color`, then `size`, then both `color` and `size`, then `shape`. How do these aesthetics behave differently for categorical vs. numerical variables?

3.  In the scatterplot of `hwy` vs. `displ`, what happens if you map a third variable to `linewidth`?

4.  What happens if you map the same variable to multiple aesthetics?

5.  Make a scatterplot of `bill_depth_mm` vs. `bill_length_mm` and color the points by `species`. What does adding coloring by species reveal about the relationship between these two variables? What about faceting by `species`?

6.  Why does the following yield two separate legends? How would you fix it to combine the two legends?

    ```{r}
    #| warning: false
    #| fig-show: hide
    ggplot(
      data = eammi2,
      mapping = aes(
        x = Stress, y = SWBscale, 
        color = sex, shape = sex
      )
    ) +
      geom_point() +
      labs(color = "Gender")
    ```

7.  Create the two following stacked bar plots. Which question can you answer with the first one? Which question can you answer with the second one?

    ```{r}
    #| fig-show: hide
    ggplot(eammi2, aes(x = sex, fill = marriage5)) +
      geom_bar(position = "fill")
    ggplot(eammi2, aes(x = marriage5, fill = sex)) +
      geom_bar(position = "fill")
    ```

8.  Run the following lines of code. Which of the two plots is saved as `mpg-plot.png`? Why?

    ```{r}
    #| eval: false
    ggplot(mpg, aes(x = class)) +
      geom_bar()
    ggplot(mpg, aes(x = cty, y = hwy)) +
      geom_point()
    ggsave("mpg-plot.png")
    ```

9.  What do you need to change in the code above to save the plot as a PDF instead of a PNG? How could you find out what types of image files would work in `ggsave()`?

10. Why does this code not work?

```{{r}}
#| error: true
my_variable <- 10
my_varıable
```

Look carefully! (This may seem like an exercise in pointlessness, but training your brain to notice even the tiniest difference will pay off when programming.)

11. Tweak each of the following R commands so that they run correctly:

```{{r}}
#| eval: false
libary(todyverse)

ggplot(dTA = mpg) + 
  geom_point(maping = aes(x = displ y = hwy)) +
  geom_smooth(method = "lm)
```

12. Press Option + Shift + K / Alt + Shift + K. What happens? How can you get to the same place using the menus?

13. Let's revisit an exercise from the @sec-ggsave. Run the following lines of code. Which of the two plots is saved as `mpg-plot.png`? Why?

```{{r}}
#| eval: false
my_bar_plot <- ggplot(mpg, aes(x = class)) +
  geom_bar()
my_scatter_plot <- ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()
ggsave(filename = "mpg-plot.png", plot = my_bar_plot)
```
